---
title: "{{< meta personal.name >}}"
subtitle: |
  ::: {.content-visible when-format="revealjs"}
  AI Leader & Educational Innovator
  :::
author: "{{< meta personal.name >}}"
date: today
date-format: "MMMM YYYY"
embed-resources: true
---

```{r setup, include=FALSE}
library(yaml)
cv_data <- read_yaml("../data/cv-data.yml")
```

::: {.content-visible unless-format="revealjs"}
## Contact Information

{{< meta personal.email >}} | {{< meta personal.phone >}}  
[LinkedIn]({{< meta personal.linkedin >}}) | [GitHub]({{< meta personal.github >}}) | [Portfolio]({{< meta personal.portfolio >}}) | [Education Platform]({{< meta personal.education_platform >}})
:::

::: {.content-visible when-format="revealjs"}
## Contact

- 📧 {{< meta personal.email >}}
- 📱 {{< meta personal.phone >}}
- 🔗 [LinkedIn]({{< meta personal.linkedin >}})
- 💻 [GitHub]({{< meta personal.github >}})
- 🌐 [Portfolio]({{< meta personal.portfolio >}})
:::

## Teaching Excellence & Innovation {.content-visible when-format="html"}

### Teaching Philosophy & Approach

- **Core Philosophy:** {{< meta teaching.philosophy.core >}}
- **Conceptual Framework:** {{< meta teaching.philosophy.framework >}}
- **Pedagogical Approach:** {{< meta teaching.philosophy.approach >}}

### Student Satisfaction & Impact

```{r satisfaction, echo=FALSE, results='asis'}
for (item in cv_data$teaching$satisfaction) {
  cat(paste0("- **", item$metric, ":** ", item$details, "\n"))
}
```

### Student Feedback Highlights

```{r feedback, echo=FALSE, results='asis'}
for (quote in cv_data$teaching$feedback) {
  cat(paste0("- *\"", quote, "\"*\n"))
}
```

## Professional Summary

{{< meta summary.main >}}

## Key Achievements

```{r achievements, echo=FALSE, results='asis'}
for (achievement in cv_data$achievements) {
  cat(paste0("- **", achievement, "**\n"))
}
```

## Leadership & Academic Experience

```{r experience, echo=FALSE, results='asis'}
for (job in cv_data$experience) {
  cat(paste0("\n### ", job$title))
  if (!is.null(job$organization)) {
    cat(paste0(" — ", job$organization))
  }
  cat("\n")
  cat(paste0("*", job$period, " | ", job$location, "*\n\n"))
  
  if (!is.null(job$responsibilities)) {
    for (resp in job$responsibilities) {
      cat(paste0("- ", resp, "\n"))
    }
  }
  
  if (!is.null(job$projects)) {
    cat("\n**Recent Projects:**\n")
    for (project in job$projects) {
      cat(paste0("- ", project, "\n"))
    }
  }
}
```

## Publications

::: {.content-visible unless-format="revealjs"}
### Books (Self-Published, Creative Commons Licensed)

```{r books, echo=FALSE, results='asis'}
for (book in cv_data$publications$books) {
  cat(paste0("- **", book$title, "** – ", book$description, "\n"))
}
```

### Doctoral Thesis

```{r thesis, echo=FALSE, results='asis'}
for (thesis in cv_data$publications$thesis) {
  cat(paste0("- **", thesis$title, "** (", thesis$year, ") – ", thesis$type, ", ", thesis$fields, ". ", thesis$description, "\n"))
}
```

### Conference Publications

```{r conferences, echo=FALSE, results='asis'}
for (conf in cv_data$publications$conferences) {
  cat(paste0("- ", conf$authors, " (", conf$year, "). \"", conf$title, ".\" *", conf$venue, "*, ", conf$location))
  if (!is.null(conf$publisher)) {
    cat(paste0(": ", conf$publisher))
  }
  if (!is.null(conf$volume)) {
    cat(paste0(" ", conf$volume))
  }
  if (!is.null(conf$pages)) {
    cat(paste0(", ", conf$pages))
  }
  cat(".\n")
}
```
:::

::: {.content-visible when-format="revealjs"}
### Selected Publications

- **4 Technical Books** (Creative Commons Licensed)
- **PhD Thesis:** Feature Extraction from Multi-modal Data (2017)
- **6+ Peer-reviewed Conference Papers** in Computer Vision & ML
:::

## Open Source Projects & Educational Tools

```{r projects, echo=FALSE, results='asis'}
for (project in cv_data$projects) {
  if (!is.null(project$description)) {
    cat(paste0("- **", project$name, "** – ", project$description))
  } else {
    cat(paste0("- **", project$name, "**"))
  }
  if (!is.null(project$year)) {
    cat(paste0(" – ", project$year))
  }
  cat("\n")
}
```

## Education

```{r education, echo=FALSE, results='asis'}
for (edu in cv_data$education) {
  cat(paste0("- **", edu$degree, "**, ", edu$field, ", ", edu$institution, ", ", edu$year))
  if (!is.null(edu$thesis)) {
    cat(paste0("  \n  *", edu$thesis, "*"))
  }
  cat("\n")
}
```

## Programming Skills

::: {.content-visible unless-format="revealjs"}
```{r skills, echo=FALSE, results='asis'}
cat(paste0("**Core Technologies:** ", paste(cv_data$skills$programming$core, collapse=" • "), "\n"))
cat(paste0("**Web Stack:** ", paste(cv_data$skills$programming$web, collapse=" • "), "\n"))
cat(paste0("**AI/ML Stack:** ", paste(cv_data$skills$programming$ai_ml, collapse=" • "), "\n"))
cat(paste0("**Educational Tech:** ", paste(cv_data$skills$programming$educational, collapse=" • "), "\n"))
```
:::

::: {.content-visible when-format="revealjs"}
### Technical Stack

- **Languages:** Python, C/C++, Java, JavaScript, SQL
- **Web:** React, Flask, FastAPI
- **AI/ML:** Langchain, TensorFlow, PyTorch
- **Educational:** Canvas LMS, Blackboard LMS
:::

## Training & Certifications {.content-visible unless-format="revealjs"}

```{r certifications, echo=FALSE, results='asis'}
for (cert in cv_data$certifications) {
  cat(paste0("- ", cert$name, ", ", cert$year, "\n"))
}
```

## Professional Service {.content-visible unless-format="revealjs"}

### Service to the Profession

```{r service-profession, echo=FALSE, results='asis'}
for (service in cv_data$service$profession) {
  cat(paste0("- **", service$role, ":** ", service$organization, ", ", service$year, "\n"))
}
```

### Service to the Community

```{r service-community, echo=FALSE, results='asis'}
for (service in cv_data$service$community) {
  cat(paste0("- **", service$role, ":** ", service$project))
  if (!is.null(service$period)) {
    cat(paste0(" (", service$period, ")"))
  } else if (!is.null(service$year)) {
    cat(paste0(" (", service$year, ")"))
  }
  cat("\n")
}
```

## Affiliations {.content-visible unless-format="revealjs"}

```{r affiliations, echo=FALSE, results='asis'}
for (affil in cv_data$affiliations) {
  cat(paste0("- **", affil$status, "**, ", affil$organization, ", ", affil$year))
  if (!is.null(affil$note)) {
    cat(paste0(" ", affil$note))
  }
  cat("\n")
}
```

## Personal Interests {.content-visible unless-format="revealjs"}

{{< meta interests >}}

## References

{{< meta references >}}